Hybrid platforms and bargaining power

### 2024-05-03 src/paper/application.tex
Rewrite and expand benchmark case

\newtheorem{definition}{Definition}
\newtheorem{observation}{Observation}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{assumption}{Assumption}

@@

\subsection{Demand}

Imagine that there is an $N_C$ mass of consumers, looking to buy one product each.
They choose from a continuum of products, which are either produced by the fringe (indexed by $F_i$), by the platform ($P_i$) and a unit mass of outside options ($0_i$).
Customer $j$ derives the following utility from buying product $T_i$:
\begin{align*}
    u^F_{{T_i}j} = v^{T_i} - p^{T_i} + \mu\epsilon^{T_i}_j \quad \text{for } T_i \in \{F, P\},
\end{align*}
where $v^T_i$ is the value of product $T_i$, $p^{T_i}$ is its price, and $\epsilon^{T_i}_j$ is an idiosyncratic taste shock.
Throughout this section I assume that the value of each product within its category is the same.
I.e., $v^T_i = v^T \, \forall\,i$.
This is to simplify the analysis, but is not crucial for the results.

$\epsilon^{T_i}_j$ is assumed to be independent and identically distributed (i.i.d.) across consumers and products, and follow a standardized Type I Extreme Value distribution.
This distributional assumption, along with the fact that each consumer consumes only one product, will lead to a tractable, logit-form demand function.

@@

Each (horizontally differentiated) product is produced by a single, monopolistically competitive (fringe) seller.
The production entails a constant marginal cost $c^{T_i}$.
As with the value, I assume that the marginal cost is the same for all products: $c^{T_i} = c^T$.
Facing the demand described in the previous paragraphs, the sellers choose their price $p^{T_i}$ to maximize profits.
The price of the outside option is normalized to zero.

@@

For both models, the previous sections describe a perfect-information extensive-form game.
As a consequence, the solution concept I use is the subgame perfect equilibrium.
As tha platform's product variety ($N_P$) is assumed to be exogenous, the only strategic variables are (1) the fringe players' entry decisions, (2) the platform's entry fee (only in the benchmark model), and (3) the prices of the products.

@@

\section{General results}
\label{sec:results}

This section presents some general result that only depend on the abstract model structure described in the previous section, and the assumptions therein.
It turns out that even within such a general setting, one can derive some interesting and non-trivial results.
\Cref{sec:example} then builds on these results to derive stronger ones under a specific demand system.

Let us start with a technical, but very useful result.
\begin{proposition}
    \label{prop:unique_equilibrium}
    Under the conditions in \cref{ass:single_crossing}, the equilibrium is unique if it exists.
\end{proposition}
The intuition behind this result is that \cref{ass:single_crossing} ensures that the total profits achieved by the fringe is either concave or hump-shaped.
Consequently, it has at most one crossing with the -- convex and increasing -- total entry cost function (for $n_F > 0$).
An example for this is shown in \cref{fig:equilibrium}.
This particular shape (concave or hump-shaped) is also the main driver for the later results about the comparative statics of equilibrium profits and entry.

\begin{figure}[ht]
    \centering
    \begin{tikzpicture}[xscale=2,yscale=2,samples=200]
        \draw[->] (0,0) -- (0,2);
        \draw[->] (0,0) -- (5.5,0) node[below] {$N_F$};

        \draw[name path=piF,domain=0.01:5.5,variable=\x,black,thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
        \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed,thick] plot ({\x},{(\x)/3});
        \node[anchor=north east] at (5,1) {$\pi_F(N_P, N_F, N_C)$};
        \node[anchor=south east] at (5,5/3) {$I_F(N_F)$};

        \fill [name intersections={of=piF and IF, name=i, total=\t}]
            [black] (i-2) circle (1pt);
        \draw[dashed] (i-2) -- (i-2 |- 0,0) node[below] {$N_F^*$};
    \end{tikzpicture}
    \caption{An example free entry equilibrium. \Cref{ass:single_crossing} states that the fringe profit function is concave or hump-shaped in $N_F$, guaranteeing at most one intersection with the linear entry cost function.}
    \label{fig:equilibrium}
\end{figure}

For the following two propositions, let us ignore free entry and equilibrium behavior, and consider the number of fringe entrants $N_F$ as fixed.
The following statement claims that the platform's profits are increasing in its own product variety.
\begin{proposition}
    \label{prop:share_of_platform}
    Assume that $f$ is continuously differentiable with respect to $N_P$ and also twice differentiable.
    Let $N_F \geq 0$.
    Then $\pi_P$ is also differentiable and
    \begin{align*}
        \frac{\partial \pi_P(N_P, N_F)}{\partial N_P} > 0.
    \end{align*}
\end{proposition}
While it might seem obvious, let us still examine what this result does and does not mean.
First, remember that $f$ is increasing in both arguments, and $N_F$ is fixed.
Therefore, an increase in $N_P$ also increases the size of the pie the participants bargain over.
This result states that the slice of the pie that the platform gets increases in this case, too.
It does not mean, however, that the \emph{relative share} of the pie that the platform gets is also bigger -- increase is only guaranteed in absolute terms.
For example, it is possible that for the new, higher value of $N_P$, the complementarities between the fringe firms become stronger, and the platform's bargaining power decreases.\footnote{
    In fact, one can show that this is the case if the cross-derivatives of $f$ are negative.
}
As this result shows, this decrease cannot be large enough to decrease the platform's profits in absolute terms.
\cref{fig:increase_N_P_platform} shows an example of this situation.

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, black, thick] {ln(1+x)};
                % \addplot[name path=tildef, dashed, black] {x};
                \node[anchor=north west] at (axis cs: .5, .4) {$N_C f(N_P, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,0.693) -- (axis cs:1,0.693);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,0.693);

                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];

                \node[anchor=north west] at (axis cs: .05, .65) {Fringe ($F$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Profit shares with $N_P$}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, dashed, black] {ln(1+x)};
                \addplot[name path=tildef, black, thick] {x};
                \node[anchor=south east] at (axis cs: 0.6, 0.6) {$N_C f(N_P', sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);

                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];

                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Profit shares with $N_P'$}
    \end{subfigure}
    \caption{Illustration of \cref{prop:share_of_platform} in the one-sided bargaining case. The right hand side figure shows a world with larger platform product variety ($N_P < N_P'$). Even though the platform's share of the total profits is smaller in relative terms in that case, it is still larger in absolute terms.}
    \label{fig:increase_N_P_platform}
\end{figure}

Next, let us look at an analogous result for the fringe firms.
As the next proposition demonstrates, in this case, the direction of the change depends on the complementarities between the fringe firms.
\begin{proposition}
    \label{prop:share_of_fringe}
    Assume that $f, w$ are twice continuously differentiable.
    Let $N_F > 0$.
    Then $\pi_F$ is also differentiable.
    \begin{align*}
        &\text{If } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0, \\
        &\text{if } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} > 0
    \end{align*}
    for all $N_P \geq 0$.
\end{proposition}
In summary, when they are mostly substitutes (the cross-derivatives of $f$ are negative), the fringe's profits decrease as a result of an increase in $N_F$.
The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its share decreases not only in relative, but also in absolute terms (as illustrated in \cref{fig:increase_N_P_fringe}).
On the other hand, when the fringe firms are mostly complements the fringe's profits increase.

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, black, thick] {sqrt(x)};
                % \addplot[name path=tildef, dashed, black] {sqrt(0.5+x)};
                \node[anchor=north west] at (axis cs: .6, 0.77) {$N_C f(0, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);

                \addplot [fill=blue, fill opacity=0.05] fill between [of=f and bottom];
                \addplot [fill=red, fill opacity=0.05] fill between [of=f and top];

                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Profit shares with $N_P = 0$}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, dashed, black] {sqrt(x)};
                \addplot[name path=tildef, black, thick] {sqrt(0.5+x)};
                \node[anchor=north west] at (axis cs: 0.05, 0.75) {$N_C f(N_P', sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1.225) -- (axis cs:1,1.225);
                \draw[name path=top_old, dashed] (axis cs:0,1) -- (axis cs:1,1);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1.225);

                \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
                \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];

                \node[anchor=north west] at (axis cs: .05, 1.17) {Fringe ($F$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Profit shares with $N_P = 0.5$}
    \end{subfigure}
    \caption{Illustration of \cref{prop:share_of_fringe} when fringe and platforrm products are substitutes. An increase in the platform's product variety increases total profits, yet, the fringe's share decreases in absolute terms.}
    \label{fig:increase_N_P_fringe}
\end{figure}

Now let us turn to equilibrium entry as a function of the platform's product variety.
The previous proposition implies an almost immediate corollary regarding the equilibrium number of fringe entrants.
\begin{corollary}
    \label{cor:fringe_entry}
    Assume that $f, w$ are twice continuously differentiable.
    Let $N_F^*$ denote the equilibrium number of fringe firms.
    Let us also assume that $N_F^* > 0$.
    Furthermore, let us assume that
    \begin{align*}
        \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0 \quad \forall n_F \leq N_F \\
        \frac{\partial^2 f(n_P, n_F)}{\partial n_F^2} < 0 \quad \forall n_F \leq N_F.
    \end{align*}
    Then the equilibrium number of fringe firms is also differentiable and
    \begin{align*}
        \frac{\partial N_F^*}{\partial N_P} < 0.
    \end{align*}
\end{corollary}
That is, the equilibrium number of entrants increases as a response to an increase in $N_P$ if the fringe firms are mostly complements, and decreases if they are mostly substitutes.
The underlyong reason is again the concave or hump-shaped fringe profit function.
If $N_F^*$ is an equilibrium, then fringe profits minus entry costs are strictly positive for all $N_F \leq N_F^*$ and strictly negative for all $N_F > N_F^*$.
Therefore, if an increase in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, equilibrium can be restored by decreasing the number of fringe entrants, and vice versa for the other case (\cref{fig:comparative_N_F}).

\begin{figure}[ht]
    \centering
    \begin{tikzpicture}[xscale=2,yscale=2,samples=200]
        \draw[->] (0,0) -- (0,2);
        \draw[->] (0,0) -- (5.5,0) node[below] {$N_F$};

        \draw[name path=piF,domain=0.01:5.5,variable=\x,black, thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
        \draw[name path=piF2,domain=0.01:5.5,variable=\x,black, thick] plot ({\x},{6*((\x)/(0.3+\x))-6*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
        \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed,thick] plot ({\x},{(\x)/3});

        \node[anchor=south] at (5,1) {$\pi_F(N_P, N_F, N_C)$};
        \node[anchor=north] at (5,0.6) {$\pi_F(N_P', N_F, N_C)$};
        \node[anchor=south east] at (5,5/3) {$I_F(N_F)$};

        \fill [name intersections={of=piF and IF, name=i, total=\t}]
            [black] (i-2) circle (1pt);
        \draw[dashed] (i-2) -- (i-2 |- 0,0) node[below] {$N_F^*$};
        \fill [name intersections={of=piF2 and IF, name=i2, total=\t}]
            [black] (i2-2) circle (1pt);
        \draw[dashed] (i2-2) -- (i2-2 |- 0,0) node[below] {${N_F^*}'$};

        \draw[->] (i-2 |- 0,0.5) -- (i2-2 |- 0,0.5);
    \end{tikzpicture}
    \caption{Illustration of comparative statics for equilibrium entry. If the change in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, equilibrium can be restored by decreasing the number of fringe entrants, and vice versa for the other case.}
    \label{fig:comparative_N_F}
\end{figure}

Finally, let us conclude this section by establishing a stronger result for a more restrictive class of profit functions.
In the following, I assume that the profit function has a specific, additive form.
Intuitively, this means that -- in terms of total profits generated -- the platform's and the fringe firms' products are substitutable to each other according to some constant ratio.
\begin{proposition}
    \label{prop:aggregate_size_additive}
    Let $f$ have the following, additive form:
    \begin{align*}
        f(N_P, N_F) = g(\alpha N_P + \beta N_F)
    \end{align*}
    where $\alpha, \beta > 0$.
    Also assume that $g$ is twice differentiable and that $g'' < 0$.
    Then
    \begin{align*}
        \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}.
    \end{align*}
    Furthermore,
    \begin{align*}
        \frac{\partial \Pi(N_P, N_F^*(N_P), N_C)}{\partial N_P} < 0.
    \end{align*}
\end{proposition}

The first part of this proposition is a stronger version of \cref{cor:fringe_entry}.
It states that, not only does the equilibrium number of fringe firms decrease as a response to an increase in $N_P$, but it establishes a lower bound for this decrease.
And, as the second part shows, this bound is sufficient to guarantee that the total size of the pie ($\Pi(N_P, N_F, N_C)$) also decreases in equilibrium.

This result has particularly strong implications in models where total profits (or total product variety) has a monotone relationship with consumer welfare, such as those in \textcite{anderson2020aggregative}.
\Cref{sec:example} also presents a demand system which satisfies this property.

\section{Logit demand}
\label{sec:example}

Let us now add more structure to the model, place the function $\Pi$ on more solid microfoundations.
The modeling strategy is heavily inspired by the logit-like demand structure and hybrid platform setting of \textcite{anderson2021hybrid}.
The setting can be thought of as a (possibly hybrid) platform market with monopolistically competing fringe firms.

>>>>

\newtheorem{definition}{Definition}
\newtheorem{observation}{Observation}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{assumption}{Assumption}

@@

\subsection{Demand}
\label{sec:demand}

Imagine that there is an $N_C$ mass of consumers, looking to buy one product each.
They choose from a continuum of products, which are either produced by the fringe (indexed by $F_i$), by the platform ($P_i$) and a unit mass of outside options ($0_i$).
Customer $j$ derives the following utility from buying product $T_i$:
\begin{align*}
    u_{T_i}^j = v_{T_i} - p_{T_i} + \mu\epsilon_{T_i}^j \quad \text{for } T_i \in \{F, P\},
\end{align*}
where $v_{T_i}$ is the value of product $T_i$, $p_{T_i}$ is its price, and $\epsilon_{T_i}^j$ is an idiosyncratic taste shock.
Throughout this section I assume that the value of each product within its category is the same.
I.e., $v_{T_i} = v_T \, \forall\,i$.
This is to simplify the analysis, but is not crucial for the results.

$\epsilon_{T_i}^j$ is assumed to be independent and identically distributed (i.i.d.) across consumers and products, and follow a standardized Type I Extreme Value distribution.
This distributional assumption, along with the fact that each consumer consumes only one product, will lead to a tractable, logit-form demand function.

@@

Each (horizontally differentiated) product is produced by a single, monopolistically competitive (fringe) seller.
The production entails a constant marginal cost $c_{T_i}$.
As with the value, I assume that the marginal cost is the same for all products: $c_{T_i} = c_T$.
Facing the demand described in the previous paragraphs, the sellers choose their price $p_{T_i}$ to maximize profits.
The price of the outside option is normalized to zero.

@@

For both models, the previous sections describe a perfect-information extensive-form game.
As a consequence, the solution concept I use is the subgame perfect equilibrium.
As the platform's product variety ($N_P$) is assumed to be exogenous, the only strategic variables are (1) the fringe players' entry decisions, (2) the platform's entry fee (only in the benchmark model), and (3) the prices of the products.

@@

% \section{General results}
% \label{sec:results}

% This section presents some general result that only depend on the abstract model structure described in the previous section, and the assumptions therein.
% It turns out that even within such a general setting, one can derive some interesting and non-trivial results.
% \Cref{sec:example} then builds on these results to derive stronger ones under a specific demand system.

% Let us start with a technical, but very useful result.
% \begin{proposition}
%     \label{prop:unique_equilibrium}
%     Under the conditions in \cref{ass:single_crossing}, the equilibrium is unique if it exists.
% \end{proposition}
% The intuition behind this result is that \cref{ass:single_crossing} ensures that the total profits achieved by the fringe is either concave or hump-shaped.
% Consequently, it has at most one crossing with the -- convex and increasing -- total entry cost function (for $n_F > 0$).
% An example for this is shown in \cref{fig:equilibrium}.
% This particular shape (concave or hump-shaped) is also the main driver for the later results about the comparative statics of equilibrium profits and entry.

% \begin{figure}[ht]
%     \centering
%     \begin{tikzpicture}[xscale=2,yscale=2,samples=200]
%         \draw[->] (0,0) -- (0,2);
%         \draw[->] (0,0) -- (5.5,0) node[below] {$N_F$};

%         \draw[name path=piF,domain=0.01:5.5,variable=\x,black,thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
%         \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed,thick] plot ({\x},{(\x)/3});
%         \node[anchor=north east] at (5,1) {$\pi_F(N_P, N_F, N_C)$};
%         \node[anchor=south east] at (5,5/3) {$I_F(N_F)$};

%         \fill [name intersections={of=piF and IF, name=i, total=\t}]
%             [black] (i-2) circle (1pt);
%         \draw[dashed] (i-2) -- (i-2 |- 0,0) node[below] {$N_F^*$};
%     \end{tikzpicture}
%     \caption{An example free entry equilibrium. \Cref{ass:single_crossing} states that the fringe profit function is concave or hump-shaped in $N_F$, guaranteeing at most one intersection with the linear entry cost function.}
%     \label{fig:equilibrium}
% \end{figure}

% For the following two propositions, let us ignore free entry and equilibrium behavior, and consider the number of fringe entrants $N_F$ as fixed.
% The following statement claims that the platform's profits are increasing in its own product variety.
% \begin{proposition}
%     \label{prop:share_of_platform}
%     Assume that $f$ is continuously differentiable with respect to $N_P$ and also twice differentiable.
%     Let $N_F \geq 0$.
%     Then $\pi_P$ is also differentiable and
%     \begin{align*}
%         \frac{\partial \pi_P(N_P, N_F)}{\partial N_P} > 0.
%     \end{align*}
% \end{proposition}
% While it might seem obvious, let us still examine what this result does and does not mean.
% First, remember that $f$ is increasing in both arguments, and $N_F$ is fixed.
% Therefore, an increase in $N_P$ also increases the size of the pie the participants bargain over.
% This result states that the slice of the pie that the platform gets increases in this case, too.
% It does not mean, however, that the \emph{relative share} of the pie that the platform gets is also bigger -- increase is only guaranteed in absolute terms.
% For example, it is possible that for the new, higher value of $N_P$, the complementarities between the fringe firms become stronger, and the platform's bargaining power decreases.\footnote{
%     In fact, one can show that this is the case if the cross-derivatives of $f$ are negative.
% }
% As this result shows, this decrease cannot be large enough to decrease the platform's profits in absolute terms.
% \cref{fig:increase_N_P_platform} shows an example of this situation.

% \begin{figure}[ht]
%     \centering
%     \begin{subfigure}[b]{0.45\textwidth}
%         \centering
%         \begin{tikzpicture}[scale=0.8]
%             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
%                 xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
%                 \addplot[name path=f, black, thick] {ln(1+x)};
%                 % \addplot[name path=tildef, dashed, black] {x};
%                 \node[anchor=north west] at (axis cs: .5, .4) {$N_C f(N_P, sN_F)$};
%                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
%                 \draw[name path=top] (axis cs:0,0.693) -- (axis cs:1,0.693);
%                 \draw[name path=right] (axis cs:1,0) -- (axis cs:1,0.693);

%                 \node[anchor=north west] at (axis cs: .05, .65) {Fringe ($F$)};
%                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
%             \end{axis}
%         \end{tikzpicture}
%         \caption{Profit shares with $N_P$}
%     \end{subfigure}
%     \begin{subfigure}[b]{0.45\textwidth}
%         \centering
%         \begin{tikzpicture}[scale=0.8]
%             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
%                 xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
%                 \addplot[name path=f, dashed, black] {ln(1+x)};
%                 \addplot[name path=tildef, black, thick] {x};
%                 \node[anchor=south east] at (axis cs: 0.6, 0.6) {$N_C f(N_P', sN_F)$};
%                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
%                 \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
%                 \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);

%                 \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
%                 \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];

%                 \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
%                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
%             \end{axis}
%         \end{tikzpicture}
%         \caption{Profit shares with $N_P'$}
%     \end{subfigure}
%     \caption{Illustration of \cref{prop:share_of_platform} in the one-sided bargaining case. The right hand side figure shows a world with larger platform product variety ($N_P < N_P'$). Even though the platform's share of the total profits is smaller in relative terms in that case, it is still larger in absolute terms.}
%     \label{fig:increase_N_P_platform}
% \end{figure}

% Next, let us look at an analogous result for the fringe firms.
% As the next proposition demonstrates, in this case, the direction of the change depends on the complementarities between the fringe firms.
% \begin{proposition}
%     \label{prop:share_of_fringe}
%     Assume that $f, w$ are twice continuously differentiable.
%     Let $N_F > 0$.
%     Then $\pi_F$ is also differentiable.
%     \begin{align*}
%         &\text{If } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0, \\
%         &\text{if } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} > 0
%     \end{align*}
%     for all $N_P \geq 0$.
% \end{proposition}
% In summary, when they are mostly substitutes (the cross-derivatives of $f$ are negative), the fringe's profits decrease as a result of an increase in $N_F$.
% The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its share decreases not only in relative, but also in absolute terms (as illustrated in \cref{fig:increase_N_P_fringe}).
% On the other hand, when the fringe firms are mostly complements the fringe's profits increase.

% \begin{figure}[ht]
%     \centering
%     \begin{subfigure}[b]{0.45\textwidth}
%         \centering
%         \begin{tikzpicture}[scale=0.8]
%             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
%                 xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
%                 \addplot[name path=f, black, thick] {sqrt(x)};
%                 % \addplot[name path=tildef, dashed, black] {sqrt(0.5+x)};
%                 \node[anchor=north west] at (axis cs: .6, 0.77) {$N_C f(0, sN_F)$};
%                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
%                 \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
%                 \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);

%                 \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($F$)};
%                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
%             \end{axis}
%         \end{tikzpicture}
%         \caption{Profit shares with $N_P = 0$}
%     \end{subfigure}
%     \begin{subfigure}[b]{0.45\textwidth}
%         \centering
%         \begin{tikzpicture}[scale=0.8]
%             \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
%                 xtick={0, 1}, ytick=\empty, axis lines=left, xlabel={$s$}]
%                 \addplot[name path=f, dashed, black] {sqrt(x)};
%                 \addplot[name path=tildef, black, thick] {sqrt(0.5+x)};
%                 \node[anchor=north west] at (axis cs: 0.05, 0.75) {$N_C f(N_P', sN_F)$};
%                 \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
%                 \draw[name path=top] (axis cs:0,1.225) -- (axis cs:1,1.225);
%                 \draw[name path=top_old, dashed] (axis cs:0,1) -- (axis cs:1,1);
%                 \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1.225);

%                 \addplot [fill=blue, fill opacity=0.05] fill between [of=tildef and bottom];
%                 \addplot [fill=red, fill opacity=0.05] fill between [of=tildef and top];

%                 \node[anchor=north west] at (axis cs: .05, 1.17) {Fringe ($F$)};
%                 \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
%             \end{axis}
%         \end{tikzpicture}
%         \caption{Profit shares with $N_P = 0.5$}
%     \end{subfigure}
%     \caption{Illustration of \cref{prop:share_of_fringe} when fringe and platforrm products are substitutes. An increase in the platform's product variety increases total profits, yet, the fringe's share decreases in absolute terms.}
%     \label{fig:increase_N_P_fringe}
% \end{figure}

% Now let us turn to equilibrium entry as a function of the platform's product variety.
% The previous proposition implies an almost immediate corollary regarding the equilibrium number of fringe entrants.
% \begin{corollary}
%     \label{cor:fringe_entry}
%     Assume that $f, w$ are twice continuously differentiable.
%     Let $N_F^*$ denote the equilibrium number of fringe firms.
%     Let us also assume that $N_F^* > 0$.
%     Furthermore, let us assume that
%     \begin{align*}
%         \frac{\partial^2 f(n_P, n_F)}{\partial n_P \partial n_F} < 0 \quad \forall n_F \leq N_F \\
%         \frac{\partial^2 f(n_P, n_F)}{\partial n_F^2} < 0 \quad \forall n_F \leq N_F.
%     \end{align*}
%     Then the equilibrium number of fringe firms is also differentiable and
%     \begin{align*}
%         \frac{\partial N_F^*}{\partial N_P} < 0.
%     \end{align*}
% \end{corollary}
% That is, the equilibrium number of entrants increases as a response to an increase in $N_P$ if the fringe firms are mostly complements, and decreases if they are mostly substitutes.
% The underlyong reason is again the concave or hump-shaped fringe profit function.
% If $N_F^*$ is an equilibrium, then fringe profits minus entry costs are strictly positive for all $N_F \leq N_F^*$ and strictly negative for all $N_F > N_F^*$.
% Therefore, if an increase in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, equilibrium can be restored by decreasing the number of fringe entrants, and vice versa for the other case (\cref{fig:comparative_N_F}).

% \begin{figure}[ht]
%     \centering
%     \begin{tikzpicture}[xscale=2,yscale=2,samples=200]
%         \draw[->] (0,0) -- (0,2);
%         \draw[->] (0,0) -- (5.5,0) node[below] {$N_F$};

%         \draw[name path=piF,domain=0.01:5.5,variable=\x,black, thick] plot ({\x},{8*((\x)/(0.3+\x))-8*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
%         \draw[name path=piF2,domain=0.01:5.5,variable=\x,black, thick] plot ({\x},{6*((\x)/(0.3+\x))-6*((\x-0.3*ln(\x+0.3)-0.361)/(\x))});
%         \draw[name path=IF,domain=0.01:5.5,variable=\x,black,dashed,thick] plot ({\x},{(\x)/3});

%         \node[anchor=south] at (5,1) {$\pi_F(N_P, N_F, N_C)$};
%         \node[anchor=north] at (5,0.6) {$\pi_F(N_P', N_F, N_C)$};
%         \node[anchor=south east] at (5,5/3) {$I_F(N_F)$};

%         \fill [name intersections={of=piF and IF, name=i, total=\t}]
%             [black] (i-2) circle (1pt);
%         \draw[dashed] (i-2) -- (i-2 |- 0,0) node[below] {$N_F^*$};
%         \fill [name intersections={of=piF2 and IF, name=i2, total=\t}]
%             [black] (i2-2) circle (1pt);
%         \draw[dashed] (i2-2) -- (i2-2 |- 0,0) node[below] {${N_F^*}'$};

%         \draw[->] (i-2 |- 0,0.5) -- (i2-2 |- 0,0.5);
%     \end{tikzpicture}
%     \caption{Illustration of comparative statics for equilibrium entry. If the change in $N_P$ decreases the fringe's profits for every $N_F \geq 0$, equilibrium can be restored by decreasing the number of fringe entrants, and vice versa for the other case.}
%     \label{fig:comparative_N_F}
% \end{figure}

% Finally, let us conclude this section by establishing a stronger result for a more restrictive class of profit functions.
% In the following, I assume that the profit function has a specific, additive form.
% Intuitively, this means that -- in terms of total profits generated -- the platform's and the fringe firms' products are substitutable to each other according to some constant ratio.
% \begin{proposition}
%     \label{prop:aggregate_size_additive}
%     Let $f$ have the following, additive form:
%     \begin{align*}
%         f(N_P, N_F) = g(\alpha N_P + \beta N_F)
%     \end{align*}
%     where $\alpha, \beta > 0$.
%     Also assume that $g$ is twice differentiable and that $g'' < 0$.
%     Then
%     \begin{align*}
%         \frac{\partial N_F^*}{\partial N_P} < -\frac{\alpha}{\beta}.
%     \end{align*}
%     Furthermore,
%     \begin{align*}
%         \frac{\partial \Pi(N_P, N_F^*(N_P), N_C)}{\partial N_P} < 0.
%     \end{align*}
% \end{proposition}

% The first part of this proposition is a stronger version of \cref{cor:fringe_entry}.
% It states that, not only does the equilibrium number of fringe firms decrease as a response to an increase in $N_P$, but it establishes a lower bound for this decrease.
% And, as the second part shows, this bound is sufficient to guarantee that the total size of the pie ($\Pi(N_P, N_F, N_C)$) also decreases in equilibrium.

% This result has particularly strong implications in models where total profits (or total product variety) has a monotone relationship with consumer welfare, such as those in \textcite{anderson2020aggregative}.
% \Cref{sec:example} also presents a demand system which satisfies this property.

% \section{Logit demand}
% \label{sec:example}
